Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-03-17 inst/examples/20170201-manuscript.Rmd
publisher analyses updated

  df <- df0
  df = subset(df, catalog == catal)
  df <- subset(df, publication_year >= minyear & publication_year <= maxyear)

  df <- subset(dfsel, publication_year >= minyear & publication_year <= maxyear)

@@

  publications[is.na(publications)] <- 0 # Set NAs to 0
  publications <- publications/timeinterval # Instead of decadal sum, use average annual output 
  dfm <- melt(publications) 
  names(dfm) <- c("Time", "Documents")
  dfm <- transform(dfm, date = as.numeric(as.character(Time)))
  ymin = min(dfm$Documents)
  ymax = max(dfm$Documents)

>>>>

  df <- df0
  df = subset(df, catalog == catal)
  df <- subset(df, publication_year >= minyear & publication_year <= maxyear)
  df <- subset(dfsel, publication_year >= minyear & publication_year <= maxyear)

@@

  publications[is.na(publications)] <- 0 # Set NAs to 0
  publications <- publications/timeinterval # Instead of decadal sum, use average annual output 
  dfm <- melt(publications) 
  names(dfm) <- c("Time", "Documents")
  dfm <- base::transform(dfm, date = as.numeric(as.character(Time)))
  ymin = min(dfm$Documents)
  ymax = max(dfm$Documents)
